### 2014-09-19 fundamentals/impl.tex
initial sentence regarding hierarchy

\subsection{Agent Interchangability}

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be comparied to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

Interchangability is accomplished by providing APIs that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. The \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

\subsection{Region/Institution/Facility hierarchy}
% (diagram)

>>>>

\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api

This approach enables ``apples-to-apples'' comparisons, something that has been 
sorely missing in previous simulators.

By making the facilities interchangeable, it combinatorically increases the 
number of scenarios that can be modeled. The user can choose to model just the 
front end or just the back end of a fuel cycle.

This is implemented with an API that focuses on treating the agents as black 
boxes.

\subsection{Regions, Institutions, and Facilities}

\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
including facilities, institutions managing those facilities, and regions. While
some simulators (TODO cite DESAE) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.
